Recent Advances in Networking

### 2013-07-23 Compiled/intro/board.tex
Full compiled
fixed minor things

\documentclass[a4paper,16pt]{article} 
\usepackage{a4wide,times,latexsym}
\usepackage[compact,tiny]{titlesec}
\usepackage{url}
\usepackage{times}
\usepackage{graphics}
\usepackage{color}
%\usepackage[pdftex]{hyperref}
\usepackage{multirow}

\pagestyle{empty}
\begin{document}

@@

\Large 
\vspace{1in}
\begin{tabular}{ll}
Ernst Biersack &	Eurecom \\
Olivier Bonaventure &	Universit$\acute{e}$ catholique de Louvain \\
Jon Crowcroft	&  University of Cambridge \\
Walid Dabbous	  & INRIA Sophia Antipolis \\
Bruce Davie	& VMware \\
Anja Feldmann	& Technische Universit$\ddot{a}$t Berlin\\
Timothy Griffin	& University of Cambridge \\
Hamed Haddadi &	Queen Mary University of London\\
Ramesh Johari	 & Stanford University\\
Srinivasan Keshav &	University of Waterloo\\
Jean-Yves Le Boudec	& $\acute{E}$cole polytechnique f$\acute{e}$d$\acute{e}$rale de Lausanne\\
Jennifer Rexford &	Princeton University\\
David Wetherall	& University of Washington\\
Walter Willinger	& AT\&T Labs Research\\
\end{tabular}
\end{center}

@@

\end{document}

>>>>

%\documentclass[a4paper,16pt]{article} 
%\usepackage{a4wide,times,latexsym}
%\usepackage[compact,tiny]{titlesec}
%\usepackage{url}
%\usepackage{times}
%\usepackage{graphics}
%\usepackage{color}
%\usepackage[pdftex]{hyperref}
%\usepackage{multirow}

%\pagestyle{empty}
%\begin{document}

@@

\Large 
\vspace{1in}
\begin{tabular}{ll}
Ernst Biersack &	Eurecom \\
Olivier Bonaventure &	Universit$\acute{e}$ catholique de Louvain \\
Jon Crowcroft	&  University of Cambridge \\
Walid Dabbous	  & INRIA Sophia Antipolis \\
Bruce Davie	& VMware \\
Anja Feldmann	& Technische Universit$\ddot{a}$t Berlin\\
Timothy Griffin	& University of Cambridge \\
Hamed Haddadi &	Queen Mary University of London\\
Ramesh Johari	 & Stanford University\\
Srinivasan Keshav &	University of Waterloo\\
Jean-Yves Le Boudec	& $\acute{E}$cole polytechnique F$\acute{e}$d$\acute{e}$rale de Lausanne\\
Jennifer Rexford &	Princeton University\\
David Wetherall	& University of Washington\\
Walter Willinger	& AT\&T Labs Research\\
\end{tabular}
\end{center}

@@

%\end{document}
